Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-11-13 paper/ms.tex
edits in the abstract and introduction

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field
size by constructing mock fields from a large cosmological N-body
simulation matching the geometries of observed fields. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm max}$ can only host
one detectable LAE with a probability $f_{\rm occ}$. The main motivation to
build such a model is to avoid the large uncertainties in the estimation of
\ly luminosities. We find that the clustering and number density information are
insufficient to impose a tight constraint on the {\bf occupation} fraction. On
the other hand the minimum mass and maximum mass are tightly
constrained to be $M_{\rm max}<10^{12}$\hMsun and
$10^{10}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$.  We also find
that all models have a narrow mass range $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ smaller than $1.0$ dex,
with the vast majority in the range $\Delta M<0.5$ dex. Already
published constraints on the mass range and occupation fraction are a sub-set of
the models we report in this \documentname. Our results present an
inconclusive response as to which is the occupation fraction for LAEs
at $z=3.1$. A precise answer requires robust physical models for the
connection between dark matter, star formation and the escape of \ly
radiation. That kind of modelling should also be able to provide a
plausible explanation for the narrow range in mass $\Delta M<1.0$ dex
derived here for the halos hosting LAEs at $z=3.1$.

@@

Lyman-$\alpha$ emitting galaxies (LAEs) have become in the last decade
a  central topic in studies of structure formation in the Universe. They 
are helpful in a diverse range of fields. LAEs can be used as probes
of reionization \citep{Dijkstra11}, tracers of large scale structure
\citep{Koehler2007},  signposts for low metallicity stellar
populations, markers of the galaxy formation process at high redshift
\citep{Dayal2009,ForeroRomero2012} and tracers of active star formation
\citep{Guaita2013}

At the same time, theoretical and observational developments have
contributed to the emergence of a paradigm to describe structure
formation in a cosmological context. In this context it is considered
that the dominant matter content of the Universe is to be found in dark
matter (DM), whereby each galaxy is hosted by larger dark matter structure
known as a halo. \citep{Peebles1980,SpringelNature05}.

Most models of galaxy formation find that halo mass can be
used to predict galaxy properties such as the stellar mass and
star formation rate \citep{Behroozi2013a}. Processes that regulate the
star formation cycle are also though to be strongly dependent on its
halo mass.  For these reasons, finding the typical dark matter halo mass
hosting LAEs represents a significant step forward to understand the
nature of this galaxy population in the context of Lambda Cold Dark
Matter ($\Lambda$CDM) paradigm.

Some theoretical approaches to this problem have been based on
ab-initio approach. Starting from the DM halo population, the
corresponding intrinsic star formation properties are inferred
together with other statistics such as the luminosity function, the
correlation function and the equivalent width distributions. Such
modelling has been implemented from analytic considerations,
semi-analytic models \citep{Garel2012, Orsi2012}and  full N-body
hydrodynamical simulations \citep{Laursen2007, Dayal2009,
  ForeroRomero2011, Yajima2012, Soler2012}.

In addition to the uncertainties in the astrophysical processes
describing star formation in galactic populations,the calculation
of the fraction of \ly photons that escape the galaxy to the observer
is another debated step. Given the resonant nature of the \ly line,
the radiative transfer of \ly is sensitive to the density,
temperature, topology and kinematics of the neutral Hydrogen in the
interstellar medium
(ISM). This problem can be tackled with Monte Carlo simulations for the
radiative transfer, however the complexity of the relevant physical
processes makes it difficult to achieve a robust consensus on what is
the theoretical expected value for the \ly escape fraction
at high redshift
\citep{Neufeld1991,Verhamme2006,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.

@@

{\bf In spite of being different fields, we find that the parameters
  describing this

the parameters in their
  correlation function are consistent with each other Nevertheless we use the ACF from this
  particular to  get a sense of a mean ACF.

>>>>

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field
size by constructing mock fields from a large cosmological N-body
simulation matching the geometries of observed fields. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm max}$ can only host
one detectable LAE with a probability $f_{\rm occ}$. The main motivation to
build such a model is to avoid the large uncertainties in the
estimation of \ly luminosities. Our main result is that the clustering
and number density information are insufficient to impose a tight
constraint on the {\bf occupation} fraction. On the other hand the
minimum mass and maximum mass can be tightly constrained to the range
$M_{\rm max}<10^{12}$\hMsun and $10^{10}\hMsun\leq M_{\rm min}\leq
10^{11.5}\hMsun$.  We also find that all models have a narrow mass
range $\Delta M \equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$
smaller than $1.0$ dex, with the vast majority in the range $\Delta
M<0.5$ dex. Already published constraints on the mass range and
occupation fraction are a sub-set of the models we report in this
\documentname. Our results present an inconclusive response as to
which is the occupation fraction for LAEs at $z=3.1$. A precise answer
requires observations on larger fields and robust physical models for
the connection between dark matter, star formation and the escape of
\ly radiation. That kind of modelling should also be able to provide a
plausible explanation for the narrow range in mass $\Delta M<1.0$ dex
derived here for the halos hosting LAEs at $z=3.1$.

@@

Lyman-$\alpha$ emitting galaxies (LAEs) are helpful in a diverse range
of subjects in extragalactic astronomy. LAEs can be
used as probes of reionization \citep{Dijkstra11}, tracers of large
scale structure \citep{Koehler2007},  signposts for low metallicity
stellar populations, markers of the galaxy formation process at high
redshift \citep{Dayal2009,ForeroRomero2012} and tracers of active star
formation \citep{Guaita2013}.

Capitalizing LAEs observations requires an understanding of
their place in the context of a given structure formarion model in a
cosmological context. Under the current paradigm the dominant matter
content of the Universe is to be found in dark matter (DM) and each
galaxy is thought to be hosted by larger dark matter structure known
as a halo. \citep{Peebles1980,SpringelNature05}.

Galaxy formation models find that halo mass predicts with high
accuracy galaxy properties such as stellar mass and star formation
rate \citep{Behroozi2013a}. This suggests that the
physical processes that regulate the star formation cycle are 
dependent on halo mass.  For that reason, finding the typical dark
matter halo mass hosting LAEs represents an advance to understand the
nature of this galaxy population in the context of Lambda Cold Dark
Matter ($\Lambda$CDM) paradigm.

Some theoretical attempts to solve this problem using an  ab-initio
approach. They start from the DM halo population to infer the
intrinsic star formation rates and \ly a luminosities. From these
values they estimate the amount of \ly photons that
escape each galaxy and compute the observed luminosity for each
galaxy. These models can predict different observables including: the
luminosity function, correlation function and the equivalent width
distributions. Such modelling has been implemented in semi-analytic
models \citep{Garel2012,   Orsi2012, Solre2012} and  full N-body
hydrodynamical simulations \citep{Laursen2007, Dayal2009,
  ForeroRomero2011, Yajima2012}.

However, there are many uncertain steps in these calculations. The
usual ones are the astrophysical processes describing star formation in galactic
populations. But the dominant uncertainty is estimating the
fraction of \ly photons that escape the galaxy, a number known as the escape
fraction. Given the resonant nature of the \ly line, the escape
fraction is sensitive to  the density, temperature, topology and
kinematics of the neutral Hydrogen in the interstellar medium
(ISM), besides the amount of dust that absorb the \ly photons. The
complex radiative transfer of \ly photons in the ISM requires Monte
Carlo simulations to be solved. Until now it has been dificult to
achieve a consensus on the expected value for the \ly escape fraction
in high redshift galaxies
\citep{Neufeld1991,Verhamme2006,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.

@@
